---
title: 'Assignment 2 - Spiders'
author: Molly Richard
output:
  html_document:
    df_print: paged
---

```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
packages_needed <- c("ggplot2", # graphics
                     "arm", # display() etc.
                     "ggfortify", # check model assumptions
                     "AICcmodavg",
                     "grid", 
                     "varhandle"
                     )
pk_to_install <- packages_needed [!( packages_needed %in% rownames(installed.packages())  )]
if(length(pk_to_install)>0 ){
  install.packages(pk_to_install,repos="http://cran.r-project.org")
}
#lapply(packages_needed, require, character.only = TRUE)
library(ggplot2)
library(readr)
library(arm)
library(ggfortify)
library(AICcmodavg)
library(grid)
library(varhandle)
```

``` {r}
spiders <- read_csv("spiders.csv")
```


```{r model}
binary_spiders <-to.dummy(spiders$status, "status")
spiders_merged <-cbind(spiders, binary_spiders)

spider_glm <- glm(status.present ~ grainsize, data= spiders_merged, family= binomial)
```

```{r graph}
ggplot(spider_glm,aes(grainsize,status.present)) +geom_point() +
  geom_smooth(method="glm", method.args=list(family="binomial"(link="logit")))+
  geom_hline(yintercept = mean(spiders_merged$status.present), linetype = "dashed") +
  labs(title="GLM, binomial count (presence/absence)")
```

Based off the visual from graph there appears to be is a positive relationship between the grain size and the presence of the species; as grain size increases there is a greater likelihood of the spider being present.

```{r coefficent}
coef(spider_glm)
confint(spider_glm)
```

```{r}
#back transform the data 
involgit <- function(x) (1+exp(-x))
invlogit(confint(spider_glm))
invlogit(coef(spider_glm))
```
To determine the linear confidence intervals, intercept, and slope, the glm has to be back transformed from the logit values.  The resulting confidence intervals do not contain zero (x=0.009, 0.674) supporting the alternative hypothesis. 

```{r}
summary(spider_glm)
```

The summary table shows the risidual deviance (30.632) is less than the null deviance (35.165), further supporting the alternative hypothesis and rejects the null hypothesis: there is a relationship between the presence of the burrowing wolf spider and the size of sand grains on beaches. 

While there is a positive relationship the p-values (0.08, 0.22) does not support this as a signficant relationship. Future conservation efforts of *Lycosa ishikariana* could be aided by the use of the equation y=0.99+16x using the inverse coefficents to determine the probability of survival on beaches with a particular grain size.

